---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


```{r,echo=FALSE, warning=FALSE}
options(xtable.comment = FALSE)
library("knitr")
library("formatR")
opts_chunk$set(message=F,comment="",tidy=T,warning=FALSE,highlight=TRUE)

```



## Loading and preprocessing the data

```{r}
data = read.csv("activity/activity.csv")
str(data)
```



## What is mean total number of steps taken per day?

1.Calculate the total number of steps taken per day

```{r}
attach(data)
s = tapply(steps, date, function(x){sum(x,na.rm = T)})
s
```

2.Make a histogram of the total number of steps taken each day

```{r}
hist(s)
```

3.Calculate and report the mean and median of the total number of steps taken per day

```{r}
mean(s)
median(s)
```


## What is the average daily activity pattern?

1.Make a time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
m = tapply(steps, interval, function(x){mean(x,na.rm = T)})
plot(names(m),m, type = "l")
```

2.Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
m[which.max(m)]
```

We can see the interval of 835 contains the maximum number of steps which is 206.2.


## Imputing missing values

1.Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)

```{r}
sum(!complete.cases(data))
```

2.Devise a strategy for filling in all of the missing values in the dataset. 

```{r}
index = !complete.cases(data)#find the index of rows which contains missing values.
new_data = data
new_data$steps[index] = m[as.character(interval[index])]#use the mean for that 5-minute interval to fill the missing values.

```

3.Create a new dataset that is equal to the original dataset but with the missing data filled in.

```{r}
head(new_data)#show a part of the new dataset
sum(!complete.cases(new_data))#check if there are still missing values
```

4.Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day

```{r}
new_s = with(tapply(steps, date, sum), data = new_data)
hist(new_s)
mean(new_s)
median(new_s)
```

These values obviously differ from the estimates from the first part of the assignment. 

The impact of imputing missing data on the estimates of the total daily number of steps is that the result looks more reasonable and the distrubition of histogram looks normal. 

## Are there differences in activity patterns between weekdays and weekends?

1.Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.

```{r}
new_data$date = as.Date(new_data$date)
head(weekdays(new_data$date))

new_data$week = ifelse( weekdays(new_data$date) %in% c("星期六","星期日"), 
        print("weekend"),
        print("weekday") )

```


2.Make a panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis).

```{r}
library(lattice)
new_m = with(aggregate(steps, list(interval, week), mean), data = new_data)
names(new_m) = c("interval", "week", "steps")
with(xyplot(steps ~ interval | week, layout = c(1, 2), type = "l"), data = new_m) 

```


